### 2016-08-28 paper.tex
Fix typo

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynolds number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results
indicate an important transitional scale threshold beyond which data should be
taken for numerical model validation, in order to stay relevant to full scale
devices.

>>>>

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynolds number thresholds but a
flatter linear regime, likely due to virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results
indicate an important transitional scale threshold beyond which data should be
taken for numerical model validation, in order to stay relevant to full scale
devices.
